Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2017-07-12 prop_letter.tex
prop_letter.tex Updating according to the meeting...

A key aspect of quantum measurement is its stochastic nature as reflected
in Born's rule\nb\citep{Born1983,peres1995quantum,544199}. Gleason's
theorem establishes the existence of a unique state (in Hilbert spaces
of dimension $\ge3$), the probabilities of whose outcomes are computed
from Born's rule assuming infinite precision\nb\citep{gleason1957,Redhead1987-REDINA,peres1995quantum}.
Then it is legitimate to question what happens when infinite precision
cannot be achieved. While a QIVPM\nb$\bar{\mu}$ might not be consistent
with a unique state\nb$\rho'$ on all projectors on a Hilbert space,
if $\bar{\mu}$ is induced by a mixed state\nb$\rho$, $\rho'$ would
close to $\rho$ when we shirk the length of intervals under some
good conditions, and recover original Gleason's theorem in the limiting
case. Since Gleason's theorem cannot apply on QIVPMs in general, it
thus remains possible that a refinement of the basic definition of
a quantum state or the computation of probability from a state may
be required when we rigorously consider the implications of finite
precision measurement.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Fuzzy Measurements}
 \label{sec:fuzzy}
A \emph{probability space} is a mathematical abstraction specifying
the necessary conditions for reasoning coherently about collections of
uncertain events\nb\cite{Kolmogorov1950}. In the quantum case, the
events of interest are specified by \emph{projection operators}
$P$. These include the empty projection\nb$\mathbb{0}$, the identity
projection\nb$\mathbb{1}$, projections of the form $\proj{\psi}$ where
$\ket{\psi}$ is a pure quantum state (an element of a Hilbert space),
sums of \emph{orthogonal} projections $P_0$ and $P_1$ such
$P_0P_1=\mathbb{0}$, and products of \emph{commuting} projections
$P_0$ and $P_1$ such $P_0P_1=P_1P_0$. In a well-defined quantum
probability
space\nb\cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010},
each event $P_{i}$ is mapped using a probability measure
$\mu : P \rightarrow [0,1]$ to a probability $\mu(P_{i})$ subject to
the following constraints: $\mu(\mathbb{0})=0$, $\mu(\mathbb{1})=1$,
$\mu\left(\mathbb{1}-P\right)=1-\mu\left(P\right)$, and for each pair
of \emph{orthogonal} projections $P_{0}$ and $P_{1}$, we have:
\begin{equation}
{\mu}\left(P_{0}+P_{1}\right)={\mu}\left(P_{0}\right)+{\mu}\left(P_{1}\right)\,.\label{eq:QuantumProbability-Addition}
\end{equation}

@@

The above axioms describe a mathematical idealization involving
infinitely precise measurements. In an actual experimental setup with
an ensemble of quantum states that are not exactly identical, and with
small imperfections and inaccuracies in measuring devices, an
experimenter might only be able to determine that the probability of
the event $\proj{0}$ is in the range $[0.49,0.51]$ instead of
precisely 0.5. The spread in this range depends on the amount of
resources (time, energy, money, etc) that are devoted to the
experiment. In the classical setting, this ``fuzziness'' is formalized
by moving to \emph{interval-valued probability measures}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Intervals of Uncertainty}
  \label{sec:Interval-Uncertainty}
We will start by reviewing IVPMs in the classical setting and then
propose our quantum generalization. In the classical setting, there
are several proposals for ``imprecise
probabilities''~\citep{Dempster1967,Shafer1976,GilboaSchmeidler1994,Marinacci1999,Weichselberger2000,JamisonLodwick2004,HuberRonchetti2009,Grabisch2016}.
Although these proposals differ in some details, they all share the
fact that the probability $\mu(E)$ of an event~$E$ is generalized from
a single real number to an interval of certainty $[\ell,r]$
where\nb$\ell$ intuitively corresponds to the strength of evidence for
the event and~$r$ corresponds to the strength of evidence against the
event. The collection of intervals used in the definition of a
probability measure must satisfy certain properties which we explain
next.

First for each interval $[\ell,r]$ we have the natural constraint
$0 \leq \ell \leq r \leq 1$ that guarantees that every element of the
interval can be interpreted as a conventional probability. We also
include $\imposs=[0,0]$ and $\necess=[1,1]$ as limiting intervals to
refer to the probability of impossible events (e.g., the null event)
and certain events (e.g., the event covering the entire sample space).
For each interval $[\ell,r]$, we also need the interval
$[1-r,1-\ell]$ so that if one interval refers to the probability of an
event, the other refers to the probability of the complement
event. For example, if we discover as a result of an experiment that
$\mu(E) = [0.2,0.3]$ for some event~$E$, we may conclude that
$\mu(\overline{E}) = [0.7,0.8]$ for the complement event
$\overline{E}$. In addition to these simple conditions, there are some
subtle conditions on how intervals are combined, which we discuss
next.

Let $E_1$ and $E_2$ be to disjoint events with probabilities
$\mu(E_1)=[\ell_1,r_1]$ and $\mu(E_2)=[\ell_2,r_2]$. A first attempt
at calculating the probability of the combined event that either $E_1$
or $E_2$ occurs might be $\mu(E_1\cup E_2) = [\ell_1+\ell_2,r_1+r_2]$. In
some cases, this is indeed a sensible definition. For example, if
$\mu(E_1)=[0.1,0.2]$ and $\mu(E_2)=[0.3,0.4]$ we get
$\mu(E_1\cup E_2) = [0.4,0.6]$. But consider an event $E$ such that
$\mu(E)=[0.2,0.3]$ and hence $\mu(\overline{E})=[0.7,0.8]$. The two
events $E$ and $\overline{E}$ are disjoint; the previous naïve way
of combining the intervals would give $\mu(E\cup\overline{E})=[0.9,1.1]$
which is not a valid probability interval. Moreover the event
$E\cup\overline{E}$ is the identity event covering the entire space; its
probability interval should be $[1,1]$ which is sharper than
$[0.9,1.1]$. The problem is that the two intervals are correlated:
there is more information in the combined event than in each event
separately. In our example, even though the true probability of
$\mu(E)$ can be in anywhere in the range $[0.2,0.3]$ and the true
probability of $\mu(\overline{E})$ can be in anywhere in the range
$[0.7,0.8]$, the values are not independent. Any value of
$\mu(E) \leq 0.25$ will force $\mu(\overline{E})\geq 0.75$. To account
for such subtleties, the axioms of interval-valued probability do not
use a strict equality for the combination of disjoint events. The
correct constraint regarding the probability of $E_1\cup E_2$ when $E_1$
and $E_2$ are disjoint is
$\mu(E_1\cup E_2) \subseteq [\ell_1+\ell_2,r_1+r_2]$ which, in combination
with the requirement for the identity event would force
$\mu(E\cup\overline{E})$ to always be $[1,1]$ irrespective of the
particular assignments of $\mu(E)$ or $\mu(\overline{E})$.

When combining non-disjoint events, there is a further subtlety whose
resolution will give the most general and final condition. For
general, non-necessarily disjoint events $E_1$ and $E_2$, we have:
\begin{equation}
\mu(E_1\cup E_2) + \mu(E_1\cap E_2) \subseteq \mu(E_1) + \mu(E_2)
\label{eq:classicalconvex}
\end{equation}
which is a generalization of the classical inclusion-exclusion
principle that uses $\subseteq$ instead of $=$ for the same reason as
before. The new condition, known as
\emph{convexity}\nb\cite{Shapley1971,GilboaSchmeidler1994,Marinacci1999,Grabisch2016},
reduces to the previously
motivated condition when the events are disjoint, i.e., when
$\mu(E_1\cap E_2) = 0$.

We now have the necessary ingredients to define QIVPMs as a
generalization of both classical IVPMs and conventional quantum
probability measures. More precisely the quantum IVPM will reduce to
the classical IVPM when the space of quantum events is restricted to
mutually commuting sub-events.

\begin{definition}[QIVPM]
  Given a collection of intervals $\mathscr{I}$ including
  $\imposs=[0,0]$ and $\necess=[1,1]$ and with addition and scalar
  multiplication defined as follows:
  \begin{subequations}\label{eq:interval-operations}
  \begin{eqnarray}
   &  & [\ell_{1},r_{1}]+[\ell_{2},r_{2}]=[\ell_{1}+\ell_{2},r_{1}+r_{2}]\textrm{ and}\\
   &  & x[\ell,r]=\begin{cases}
  [x\ell,xr] & \textrm{for }x\ge0\,;\\{}
  [xr,x\ell] & \textrm{for }x\le0\,,
  \end{cases}
  \end{eqnarray}
  \end{subequations}
  a QIVPM $\bar{\mu}$ is an assignment of an interval to each event
  (projection operator) subject to the following constraints:
  $\bar{\mu}(\mathbb{0})=\left[0,0\right]$,
  $\bar{\mu}(\mathbb{1})=\left[1,1\right]$,
  $\bar{\mu}\left(\mathbb{1}-P\right)=\left[1,1\right]-\bar{\mu}\left(P\right)$,
  and for each pair of \emph{commuting} projections $P_0$ and $P_1$,
  we have:
\begin{equation}
\bar{\mu}\left(P_{0}+P_{1}-P_{0}P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)
\label{eq:QuantumInterval-valuedProbability-Inclusion}
\end{equation}
\end{definition}
The first three constraints are the direct counterpart of the
corresponding ones for conventional probability measures. With the
understanding that the union of classical sets $E_1\cup E_2$ is replaced
by $P_0+P_1-P_0P_1$ in the case of projection operators~\cite{Griffiths2003}, the last
condition, Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}), is
a direct counterpart of Eq.~(\ref{eq:classicalconvex}).

Contrary to the case with conventional quantum probability spaces,
there is generally no unique state consistent with a QIVPM. Given
observations done with finite resources, the probabilities become
intervals, and we say a state\nb$\rho$ is consistent with $\bar{\mu}$ on
a projector\nb$P$ if
$\mu_{\rho}^{\mathrm{B}}\left(P\right)\in\bar{\mu}\left(P\right)$, and
denoted by
$\rho\in\coreBorn\left(\bar{\mu},\left\{ P\right\} \right)$,
where $\mu_{\rho}^{\mathrm{B}}\left(P\right)=\Tr\left(\rho P\right)$
is the probability that the event\nb$P$ happens determined by the
Born rule\nb\cite{Born1983,peres1995quantum,544199}.
Moreover, $\rho\in\coreBorn\left(\bar{\mu},S\right)$ means~$\rho$ is
consistent with $\bar{\mu}$ on every projector in $S$.

Quantum IVPMs become classical IVPMs when the space of events includes
only mutually commuting events, where $\events'\subseteq\events$
is called a sub-event space if it satisfies the following conditions.
\begin{itemize}
\item $\left\{ \mathbb{0},\mathbb{1}\right\} \subseteq\events'$.
\item For any projection\nb$P\in\events'$, we have $\mathbb{1}-P\in\events'$. 
\item For each pair of orthogonal projections\nb$P_0 \in \events'$ and
  $P_1 \in \events'$, we have $(P_0 + P_1) \in \events'$. 
\end{itemize}

For example, assuming the three intervals \imposs, \necess, and
$\unknown=\left[0,1\right]$, then:
\begin{equation}
\bar{\mu}_{1}\left(P\right)=\begin{cases}
\necess\,, & \text{if }P=\mathbb{1}\text{ ;}\\
\imposs\,, & \text{if }P=\mathbb{0}\text{ ;}\\
\unknown\,, & \text{otherwise,}
\end{cases}\label{eq:no-information-IVPM}
\end{equation}
is a QIVPM. This measure represents the beliefs of an experimenter
with no prior knowledge about the particular quantum system in
question; any quantum state would be consistent with $\bar{\mu}_{1}$
on any projectors. We have that
$\events_{0}=\left\{ \mathbb{0},\proj{0},\proj{1},\mathbb{1}\right\} $
is a commuting sub-event space. Restricting $\bar{\mu}_{1}$ on
$\events_{0}$, $\bar{\mu}_{1}|_{\events_{0}}$, gives a classical
IVPM~$\bar{\mu}_{2}$:
\begin{equation}
\begin{aligned}\bar{\mu}_{2}(\mathbb{0}) & =\imposs & \bar{\mu}_{2}(\proj{0}) & =\unknown\\
\bar{\mu}_{2}(\mathbb{1}) & =\necess & \bar{\mu}_{2}(\proj{1}) & =\unknown
\end{aligned}
\,.
\end{equation}
If we identify the density matrices\nb$\proj{0}$ and $\proj{1}$ as
the head and the tail of a coin, respectively, then $\bar{\mu}_{2}$
represents that an experimenter knows nothing about a coin before
she tosses it. Moreover, for each $p\in\left[0,1\right]$, the mixed
state\nb$p\proj{0}+\left(1-p\right)\proj{1}$ represents a classical
coin with probability\nb$p$ to get head, and $p\proj{0}+\left(1-p\right)\proj{1}$
is consistent with $\bar{\mu}_{2}$ on $\events_{0}$ because any
classical coin should be consistent with the situation where an experimenter
has no prior knowledge.

@@

Our first result is that a QIVPM cannot be cryptodeterministic in the
sense of Peres\nb\cite{PeresRon1988,peres1995quantum}. We will adapt
the proof of the Kochen-Specker theorem~\cite{kochenspecker1967,
  peres1995quantum,Redhead1987-REDINA,Griffiths2003} to show that it
is, in general, impossible to just have the two intervals \imposs\ and
\necess: every QIVPM must be parameterized by a collection of
intervals that includes at least one additional ``fuzzy'' interval and
some events must be associated with such uncertain intervals. The
significance of this observation is that the uncertainty in the
intervals is, in contrast to the classical case, \emph{a fundamental
  part of quantum theory}. There are in fact two sources of
uncertainty: one due to the finite measurement resources and one due
to complementarity which requires every quantum framework to be truly
probabilistic.

We will proceed by assuming a cryptodeterministic QIVMP $\bar{\mu}$
and derive a contradiction using the following nine ``Mermin-Peres square''
observables $\mathbf{O}_{ij}$\nb\cite{Mermin1990Simple,peres1995quantum}:
\begin{center}
\begin{tabular}{|c|c|c|}
\hline 
$\mathbb{1}\otimes\sigma_{z}$  & $\sigma_{z}\otimes\mathbb{1}$  & $\sigma_{z}\otimes\sigma_{z}$ \tabularnewline
\hline 
$\sigma_{x}\otimes\mathbb{1}$  & $\mathbb{1}\otimes\sigma_{x}$  & $\sigma_{x}\otimes\sigma_{x}$ \tabularnewline
\hline 
$\sigma_{x}\otimes\sigma_{z}$  & $\sigma_{z}\otimes\sigma_{x}$  & $\sigma_{y}\otimes\sigma_{y}$ \tabularnewline
\hline 
\end{tabular}
\par\end{center}

>>>>

A key aspect of quantum measurement is its stochastic nature as reflected
in Born's rule\nb\citep{Born1983,peres1995quantum,544199}. Gleason's
theorem establishes the existence of a unique state (in Hilbert spaces
of dimension $\ge3$), the probabilities of whose outcomes are computed
from Born's rule assuming infinite precision\nb\citep{gleason1957,Redhead1987-REDINA,peres1995quantum}.
Then it is legitimate to question what happens when infinite precision
cannot be achieved. While a QIVPM\nb$\bar{\mu}$ might not be consistent
with a unique state\nb$\rho'$ on all projectors on a Hilbert space,
if $\bar{\mu}$ is induced by a mixed state\nb$\rho$, $\rho'$ would
close to $\rho$ when we shrink the length of intervals under some
good conditions, and recover original Gleason's theorem in the limiting
case.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Fuzzy Measurements}
 \label{sec:fuzzy}
A \emph{probability space} is a mathematical abstraction specifying
the necessary conditions for reasoning coherently about collections of
uncertain events\nb\cite{Kolmogorov1950}. In the quantum case, the
events of interest are specified by \emph{projection operators}
$P$. These include the empty projection\nb$\mathbb{0}$, the identity
projection\nb$\mathbb{1}$, projections of the form $\proj{\psi}$ where
$\ket{\psi}$ is a pure quantum state (an element of a Hilbert space),
sums of \emph{orthogonal} projections $P_0$ and $P_1$ with
$P_0P_1=\mathbb{0}$, and products of \emph{commuting} projections
$P_0$ and $P_1$ with $P_0P_1=P_1P_0$. In a well-defined quantum
probability
space\nb\cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010},
each event $P_{i}$ is mapped to a probability using a probability measure
$\mu : P \rightarrow [0,1]$ to a probability $\mu(P_{i})$. We impose
the following constraints: $\mu(\mathbb{0})=0$, $\mu(\mathbb{1})=1$,
$\mu\left(\mathbb{1}-P\right)=1-\mu\left(P\right)$, and for each pair
of \emph{orthogonal} projections $P_{0}$ and $P_{1}$, standard probability
measures obey
\begin{equation}
{\mu}\left(P_{0}+P_{1}\right)={\mu}\left(P_{0}\right)+{\mu}\left(P_{1}\right)\,.\label{eq:QuantumProbability-Addition}
\end{equation}

@@

The above axioms describe a mathematical idealization involving
infinitely precise measurements. In an actual experimental setup with
an ensemble of quantum states that are not exactly identical, and with
small imperfections and inaccuracies in measuring devices, an
experimenter might only be able to determine that the probability of
the event $\proj{0}$ is in the range $[0.49,0.51]$ instead of
precisely 0.5. The spread in this range depends on the amount of
resources (time, energy, money, etc.) that are devoted to the
experiment. In the classical setting, this ``fuzziness'' can be formalized
by moving to \emph{interval-valued probability measures}, which we explore in
the next section, along with our proposed extension to the quantum domain.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Intervals of Uncertainty}
  \label{sec:Interval-Uncertainty}
We will start by reviewing IVPMs in the classical setting and then
propose our quantum generalization. In the classical setting, there
are several proposals for ``imprecise
probabilities''~\citep{Dempster1967,Shafer1976,GilboaSchmeidler1994,Marinacci1999,Weichselberger2000,JamisonLodwick2004,HuberRonchetti2009,Grabisch2016}.
Although these proposals differ in some details, they all share the
fact that the probability $\mu(E)$ of an event~$E$ is generalized from
a single real number to an interval\nb$[\ell,r]$
where\nb$\ell$ intuitively corresponds to the strength of evidence for
the event and~$1-r$ corresponds to the strength of evidence against the
event. The collection of intervals used in the definition of a
probability measure must satisfy certain properties that we explain
next.

First, for each interval $[\ell,r]$ we have the natural constraint
$0 \leq \ell \leq r \leq 1$ that guarantees that every element of the
interval can be interpreted as a conventional probability. We also
include $\imposs=[0,0]$ and $\necess=[1,1]$ as limiting intervals to
refer to the probability of impossible events (e.g., the null event)
and certain events (e.g., the event covering the entire sample space).
For each interval $[\ell,r]$, we also need the interval
$[1-r,1-\ell]$ so that if one interval refers to the probability of an
event, the other refers to the probability of the event's complement.
For example, if we discover as a result of an experiment that
$\mu(E) = [0.2,0.3]$ for some event~$E$, we may conclude that
$\mu(\overline{E}) = [0.7,0.8]$ for the complementary event
$\overline{E}$. In addition to these simple conditions, there are some
subtle conditions on how intervals are combined, which we discuss
next.

Let $E_1$ and $E_2$ be two disjoint events with probabilities
$\mu(E_1)=[\ell_1,r_1]$ and $\mu(E_2)=[\ell_2,r_2]$. A first attempt
at calculating the probability of the combined event that \emph{either} $E_1$
or $E_2$ occurs might be $\mu(E_1\cup E_2) = [\ell_1+\ell_2,r_1+r_2]$. In
some cases, this is indeed a sensible definition. For example, if
$\mu(E_1)=[0.1,0.2]$ and $\mu(E_2)=[0.3,0.4]$ we get
$\mu(E_1\cup E_2) = [0.4,0.6]$. But consider an event $E$ such that
$\mu(E)=[0.2,0.3]$ and hence $\mu(\overline{E})=[0.7,0.8]$. The two
events $E$ and $\overline{E}$ are disjoint; the previous naïve way
of combining the intervals would give $\mu(E\cup\overline{E})=[0.9,1.1]$
which is not a valid probability interval. Moreover the event
$E\cup\overline{E}$ is the identity event covering the entire space; its
probability interval should be $[1,1]$ which is sharper than
$[0.9,1.1]$. The problem is that the two intervals are correlated:
there is more information in the combined event than in each event
separately. In our example, even though the true probability of
$\mu(E)$ can be anywhere in the range $[0.2,0.3]$ and the true
probability of $\mu(\overline{E})$ can be in anywhere in the range
$[0.7,0.8]$, the values are not independent. Any value of
$\mu(E) \leq 0.25$ will force $\mu(\overline{E})\geq 0.75$. To account
for such subtleties, the axioms of interval-valued probability do not
use a strict equality for the combination of disjoint events. The
correct constraint regarding the probability of $E_1\cup E_2$ when $E_1$
and $E_2$ are disjoint is
$\mu(E_1\cup E_2) \subseteq [\ell_1+\ell_2,r_1+r_2]$ which, in combination
with the requirement for the identity event would force
$\mu(E\cup\overline{E})$ to always be $[1,1]$ irrespective of the
particular assignments of $\mu(E)$ or $\mu(\overline{E})$.

When combining non-disjoint events, there is a further subtlety whose
resolution will give us one final general condition. For
general, not necessarily disjoint, events $E_1$ and $E_2$, we have:
\begin{equation}
\mu(E_1\cup E_2) + \mu(E_1\cap E_2) \subseteq \mu(E_1) + \mu(E_2)
\label{eq:classicalconvex}
\end{equation}
which is a generalization of the classical inclusion-exclusion
principle that uses $\subseteq$ instead of $=$ for the same reason as
before. The new condition, known as
\emph{convexity}\nb\cite{Shapley1971,GilboaSchmeidler1994,Marinacci1999,Grabisch2016},
reduces to the previously
motivated condition when the events are disjoint, i.e., when
$\mu(E_1\cap E_2) = 0$.

We now have the necessary ingredients to define QIVPMs as a
generalization of both classical IVPMs and conventional quantum
probability measures. We will assume that the quantum IVPM will reduce to
the classical IVPM when the space of quantum events is restricted to
mutually commuting sub-events.

\begin{definition}[QIVPM]
  Assume a collection of intervals $\mathscr{I}$ including
  $\imposs=[0,0]$ and $\necess=[1,1]$ with addition and scalar
  multiplication defined as follows:
  \begin{subequations}\label{eq:interval-operations}
  \begin{eqnarray}
   &  & [\ell_{1},r_{1}]+[\ell_{2},r_{2}]=[\ell_{1}+\ell_{2},r_{1}+r_{2}]\textrm{ and}\\
   &  & x[\ell,r]=\begin{cases}
  [x\ell,xr] & \textrm{for }x\ge0\,;\\{}
  [xr,x\ell] & \textrm{for }x\le0\,.
  \end{cases}
  \end{eqnarray}
  \end{subequations}
  Then we take a QIVPM\nb$\bar{\mu}$ to be an assignment of an interval to each
  event (projection operator\nb$P$) subject to the following constraints:
  \begin{subequations}\label{eq:QIVPM-constraints}
  \begin{eqnarray}
   &  & \bar{\mu}(\mathbb{0})=\left[0,0\right]\,,\\
   &  & \bar{\mu}(\mathbb{1})=\left[1,1\right]\,,\\
   &  & \bar{\mu}\left(\mathbb{1}-P\right)=\left[1,1\right]-\bar{\mu}\left(P\right)\,,
  \end{eqnarray}
  \end{subequations}
  and satisfying for each pair of \emph{commuting} projections $P_0$ and $P_1$,
  ($P_0P_1=P_1P_0$)
\begin{equation}
\bar{\mu}\left(P_{0}+P_{1}-P_{0}P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)\,.
\label{eq:QuantumInterval-valuedProbability-Inclusion}
\end{equation}
\end{definition}
The first three constraints\nb(\ref{eq:QIVPM-constraints}) are the direct
counterpart of the corresponding ones for conventional interval probability
measures.
With the understanding that the union of classical sets $E_1\cup E_2$ is replaced
by $P_0+P_1-P_0P_1$ in the case of quantum projection
operators~\cite{Griffiths2003}, the last condition, Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}), is
a direct counterpart of Eq.~(\ref{eq:classicalconvex}).

Contrary to the case with conventional quantum probability spaces,
there is generally no unique state consistent with a QIVPM. Given
observations done with finite resources, the probabilities become
intervals, and we say a state\nb$\rho$ is consistent with the
measure\nb$\bar{\mu}$ acting on a projector\nb$P$ if
$\mu_{\rho}^{\mathrm{B}}\left(P\right)\in\bar{\mu}\left(P\right)$, and
denoted by
$\rho\in\coreBorn\left(\bar{\mu},\left\{ P\right\} \right)$,
where $\mu_{\rho}^{\mathrm{B}}\left(P\right)=\Tr\left(\rho P\right)$
is the probability that the event\nb$P$ happens determined by the
Born rule\nb\cite{Born1983,peres1995quantum,544199}.
$\rho\in\coreBorn\left(\bar{\mu},S\right)$ means~$\rho$ is
consistent with $\bar{\mu}$ on every projector in $S$.

Quantum IVPMs become classical IVPMs when the space of events includes
only mutually commuting events. We define $\events'\subseteq\events$
to be a sub-event space if it satisfies the following conditions.
\begin{itemize}
\item $\left\{ \mathbb{0},\mathbb{1}\right\} \subseteq\events'$.
\item For any projection\nb$P\in\events'$, we have $\mathbb{1}-P\in\events'$. 
\item For each pair of orthogonal projections\nb$P_0 \in \events'$ and
  $P_1 \in \events'$, we have $(P_0 + P_1) \in \events'$. 
\end{itemize}

For example, assuming the three intervals $\imposs=\left[0,0\right]$,
$\necess=\left[1,1\right]$, and $\unknown=\left[0,1\right]$, then:
\begin{equation}
\bar{\mu}_{1}\left(P\right)=\begin{cases}
\necess\,, & \text{if }P=\mathbb{1}\text{ ;}\\
\imposs\,, & \text{if }P=\mathbb{0}\text{ ;}\\
\unknown\,, & \text{otherwise,}
\end{cases}\label{eq:no-information-IVPM}
\end{equation}
is a QIVPM. This measure represents the beliefs of an experimenter
with no prior knowledge about the particular quantum system in
question; any quantum state would be consistent with $\bar{\mu}_{1}$
on any projectors. We have that
$\events_{0}=\left\{ \mathbb{0},\proj{0},\proj{1},\mathbb{1}\right\} $
is a commuting sub-event space. Restricting $\bar{\mu}_{1}$ to
$\events_{0}$, $\bar{\mu}_{1}|_{\events_{0}}$, gives a classical
IVPM~$\bar{\mu}_{2}$:
\begin{equation}
\begin{aligned}\bar{\mu}_{2}(\mathbb{0}) & =\imposs & \bar{\mu}_{2}(\proj{0}) & =\unknown\\
\bar{\mu}_{2}(\mathbb{1}) & =\necess & \bar{\mu}_{2}(\proj{1}) & =\unknown
\end{aligned}
\,.
\end{equation}
If we identify the density matrices\nb$\proj{0}$ and $\proj{1}$ as
the head and the tail of a coin, respectively, then $\bar{\mu}_{2}$
represents the situation in which that an experimenter knows nothing about a
coin before she tosses it. Moreover, for each $p\in\left[0,1\right]$, the mixed
state\nb$p\proj{0}+\left(1-p\right)\proj{1}$ represents a classical
coin with probability\nb$p$ to get heads, and
$p\proj{0}+\left(1-p\right)\proj{1}$ is consistent with $\bar{\mu}_{2}$ on $\events_{0}$ because any
classical coin should be consistent with the situation for which an experimenter
has no prior knowledge.

@@

Our first result is that a QIVPM is consistent with the inability to avoid
uncertainty found in conventional infinite precise quantum
mechanics\nb\cite{PeresRon1988,peres1995quantum}. We will adapt
the proof of the Kochen-Specker theorem~\cite{kochenspecker1967,
  peres1995quantum,Redhead1987-REDINA,Griffiths2003} to show that it
is, in general, impossible to have just the two intervals \imposs\ and
\necess: every QIVPM must be parameterized by a collection of
intervals that includes at least one additional ``fuzzy'' interval and
some events must be associated with such uncertain intervals. The
significance of this observation is that the uncertainty in the
intervals is, in contrast to the classical case, \emph{a fundamental
  part of quantum theory}. There are in fact two sources of
uncertainty: one due to the finite measurement resources and one due
to complementarity, which requires every quantum framework to be truly
probabilistic.

We will proceed by assuming a QIVMP $\bar{\mu}$
and derive a contradiction using the following nine ``Mermin-Peres square''
observables $\mathbf{O}_{ij}$\nb\cite{Mermin1990Simple,peres1995quantum}:
\begin{center}
\begin{tabular}{|c|c|c|}
\hline 
$\mathbb{1}\otimes\sigma_{z}$  & $\sigma_{z}\otimes\mathbb{1}$  & $\sigma_{z}\otimes\sigma_{z}$ \tabularnewline
\hline 
$\sigma_{x}\otimes\mathbb{1}$  & $\mathbb{1}\otimes\sigma_{x}$  & $\sigma_{x}\otimes\sigma_{x}$ \tabularnewline
\hline 
$\sigma_{x}\otimes\sigma_{z}$  & $\sigma_{z}\otimes\sigma_{x}$  & $\sigma_{y}\otimes\sigma_{y}$ \tabularnewline
\hline 
\end{tabular}\,,
\par\end{center}
